### 2021-11-01 text/outline/draft.tex
finish implementing gene's edits (in all sections but theory)

The genomics literature has produced several applied methods for single-cell CRISPR screen analysis. In a prior work we developed SCEPTRE \cite{Barry2020}, a custom implementation of the conditional randomization test \cite{Candes2018, Liu2021} tailored to single-cell CRISPR screen data. SCEPTRE tests whether a given perturbation is associated with the change in expression of a given gene, adjusting for sources of confounding and ensuring robustness to expression model misspecification. Other applied methods for single-cell CRISPR screen analysis include MIMOSCA \cite{Dixit2016} and scMAGeCK \cite{Yang2019}. These methods, like SCEPTRE, focus on hypothesis testing (rather than estimation), but unlike SCEPTRE, they ignore the countedness of the data and are unable to handle confounders. In this work we tackle a set of analysis challenges that are complimentary to the challenges addressed by SCEPTRE. Most importantly, we seek to \textit{estimate} (with confidence) the effect size of a perturbation on gene expression change, \blue{a statistical objective that is unattainable within the nonparameteric hypothesis testing framework of SCEPTRE.}

@@

\section{Thresholding method}
\blue{In their original analysis of the data, Gasperini and Xie imputed perturbation identities onto the cells by thresholding the gRNA counts. In this section we study the thresholding method from empirical and theoretical perspectives, uncovering several limitations of the approach. We investigate the specific version of the thresholding method used by Gasperini, which involved a thresholding step and a follow-up negative binomial regression step. (Xie implemented a slightly different and, in our view, less principled version of thresholding, which we do not review here.)}

@@

\item[3.] Compute a $p$-value and confidence interval for the target of inference $\beta^m_1$.
\end{itemize}

% Setting $\gamma_m^T$ to zero and exponentiating both sides of (\ref{thresh_glm}), we obtain
% $$\mu_i = \left(e^{\beta^m_0 + \beta^m_1\hat{p}_i}\right) l^m_i.$$ The mean expression of unperturbed cells $\mu_i(0)$ is
% $$\mu_i(0) = e^{\beta^m_0} l_i^m,$$ and the mean expression in perturbed cells is
% $$ \mu_i(1) = e^{\beta^m_1} e^{\beta^m_0} l^m_i.$$ Therefore,
% $$ \beta^m_1 = \log\left(\frac{\mu_i(1)}{\mu_i(0)}\right).$$
% We use library size $l_i^m$

>>>>

The genomics literature has produced several applied methods for single-cell CRISPR screen analysis. In a prior work we developed SCEPTRE \cite{Barry2020}, a custom implementation of the conditional randomization test \cite{Candes2018, Liu2021} tailored to single-cell CRISPR screen data. SCEPTRE tests whether a given perturbation is associated with the change in expression of a given gene, adjusting for sources of confounding and ensuring robustness to expression model misspecification. Other applied methods for single-cell CRISPR screen analysis include MIMOSCA \cite{Dixit2016} and scMAGeCK \cite{Yang2019}. These methods, like SCEPTRE, focus on hypothesis testing (rather than estimation), but unlike SCEPTRE, they ignore the countedness of the data and are unable to handle confounders. In this work we tackle a set of analysis challenges that are complimentary to the challenges addressed by SCEPTRE. Most importantly, we seek to \textit{estimate} (with confidence) the effect size of a perturbation on gene expression change, \blue{a statistical objective unattainable within the nonparameteric hypothesis testing framework of SCEPTRE.}

@@

\section{Thresholding method}
\blue{In this section we study the thresholding method from empirical and theoretical perspectives, uncovering several limitations of the approach. Gasperini and Xie both imputed perturbation identities onto cells via thresholding, but they carried out subsequent differential expression analyses in different ways: Gasperini ran negative binomial regressions, while Xie conducted nonparametric tests of independence. These two approaches pose similar challenges, but we investigate the regression-based version of the thresholding method here, as it relates most closely to GLM-EIV.}

@@

\item[3.] Compute a $p$-value and confidence interval for the target of inference $\beta^m_1$.
\end{itemize}
\blue{We include the library size $l^m_i$ as an offset term in (\ref{thresh_glm}) so that $\beta^m_0 + \beta^m_1 \hat{p}_i + \gamma^T_m z_i$ can be interpreted as a relative expression: exponentiating both sides of (\ref{thresh_glm}), we obtain
$$\mu_i = \exp \left( \beta^m_0 + \beta^m_1 \hat{p}_i + \gamma^T_m z_i \right) l_i^m.$$ We see that $\exp \left( \beta^m_0 + \beta^m_1 \hat{p}_i + \gamma^T_m z_i \right)$ is the \textit{fraction} of transcripts in the cell produced by the gene under consideration.}
